\LARGE \bf Reactive Trajectory Planning and Tracking for Pedestrian-Aware Autonomous Driving on Fixed Paths

### 2016-01-21 root.tex
removed paper2, renamed paper1 to root as per IEEE convention

\subsection{2d to 1d conversion}

@@

\subsection{Control Reference Signal} \label{sec:controlreferencesignal}

\begin{figure}[thpb]
  \centering
  \includegraphics[width=0.5\columnwidth]{graphics/PathProjectionSlice.png}
  \caption{car to s coord with additional points}
  \label{fig:cartos2}
\end{figure}

@@

\section{Reactive Subsystem} \label{sec:reactiveubsystem}

\begin{figure}[thpb]
\centering
  \subfigure[In NORMAL mode, RSTOP is now triggered.]{\includegraphics[width=1.0\columnwidth]{graphics/RSTOP_NORMAL_time_to_stop.png}}
  \\
  \subfigure[RSTOP diagram showing bounds for revising the RSTOP trajectory.]{\includegraphics[width=1.0\columnwidth]{graphics/RSTOP_RSTOP.png}}
  \\
  \subfigure[Resuming after stop sign]{\includegraphics[width=1.0\columnwidth]{graphics/RSTOP_RESUME.png}}
  \caption{Reactive behavior to pedestrain}
  \label{fig:react}
\end{figure}

@@

For reactive stopping, if there are multiple pedestrian ahead, we only consider the
closest pedestrian. That pedestrian is projected on the path of the car to determine the
required braking distance. The stopping trajectory is similar to rest of profile,
and consists of a single segment with 3 phases as shown in Figure \ref{fig:3phase}. 
The trajectory planner uses total distance as parameter, and is not suitable for
our purpose as the end speed constraints are not met. So we reformulate and 
replace $L$ with $v_f$ as hard constraint.

@@

Once a pedestrian enters the stop zone, we need to plan, and execute RSTOP trajectory.
When available distance <= “required” distance, we increase acceleration, jerk peaks to
match available distance.

>>>>

@@

@@

\begin{figure}[thpb]
\centering
  \subfigure[In NORMAL mode, RSTOP is now triggered.]{\includegraphics[width=1.0\columnwidth]{graphics/RSTOP_NORMAL_time_to_stop.png}}
  \\
  \subfigure[RSTOP diagram showing bounds for revising the RSTOP trajectory.]{\includegraphics[width=1.0\columnwidth]{graphics/RSTOP_RSTOP.png}}
  \\
  \subfigure[PSTOP diagram showing bounds for reverting to NORMAL mode.]{\includegraphics[width=1.0\columnwidth]{graphics/RSTOP_RESUME.png}}
  \caption{Reactive behavior to pedestrain}
  \label{fig:react}
\end{figure}

@@

For reactive stopping, if there are multiple pedestrian ahead, we only consider the
closest pedestrian.
That pedestrian is projected on the path of the car to determine the required braking distance.
The stopping trajectory is similar to rest of profile, and consists of a single segment with 3 phases as shown in Figure \textbf{reference! include 3 phase full spec profile?}. 
The trajectory planner uses total distance as parameter, and is not suitable for our purpose as the end speed constraints are not met. So we reformulate and replace $L$ with $v_f$ as hard constraint.

@@

Once a pedestrian enters the stop zone, we need to plan, and execute RSTOP trajectory.
When available distance is less than “required” distance, we increase acceleration, jerk peaks to match available distance.
